---
title: "Supplementary Appendix B: 10,000 vs. 1,000 replications"
author: "Felix Schönbrodt"
date: "`r Sys.Date()`"
output: pdf_document
classoption: landscape
---


```{r setup, include=FALSE}
library(knitr)
library(ggplot2)

```


```{r echo=FALSE, cache=TRUE, results="hide"}
## ======================================================================
## This file loads the results of the meta-analyses (which were generated in 2-analysisFramework.R)
## and computes summaries of them (such as mean error, MSE, coverage, etc.)
## ======================================================================

# load the results files which were generated in 2-analysisFramework.R,
# combine them into one large data frame
analysisFiles <- list.files("analysisParts", pattern=".*\\.RData", full.names=TRUE)


# loop through all files
res_list <- list()
for (f in analysisFiles) {
  print(f)
  load(f)	# the simulation data frame always is called "res"
  
  # make pcurve.evidence and pcurve.lack two separate methods
  res$method <- as.character(res$method)
  res$method[res$method=="pcurve"] <- paste0("pcurve.", res$term[res$method=="pcurve"])
  
  # Slice into 10 batches of 1000 simulations
  res$simBatch <- factor(as.numeric(cut(res$id, 10)))
  
  res_list[[f]] <- res
}
res.final <- bind_rows(res_list)
rm(res_list)
str(res.final)


# Show conditions
tab <- res.final %>% group_by(k, delta, selProp, tau) %>% summarise(n.MA=length(unique(id)))
print(tab, n=50)


# Reshape to wide format
res.wide <- res.final %>% filter(term %in% c("b0", "kSig")) %>% dcast(id + condition + simBatch + k + delta + qrpEnv + selProp + tau + method + term ~ variable, value.var="value")

# get id's with kSig >= 4
incl <- res.wide %>% filter(term=="kSig") %>% group_by(id) %>% summarise(kSig_include = estimate >= 4)
incl.ids <- incl$id[incl$kSig_include == TRUE]

# Set p-curve and p-uniform to NA where kSig < 4
res.wide$estimate[!res.wide$id %in% incl.ids & res.wide$method %in% c("puniform", "pcurve.b0") & res.wide$term == "b0"] <- NA


# define some meaningful labels for the plots
res.wide$delta.label <- factor(res.wide$delta, levels=unique(res.wide$delta), labels=paste0("delta = ", unique(res.wide$delta)))
res.wide$k.label <- factor(res.wide$k, levels=sort(unique(res.wide$k)), labels=paste0("k = ", sort(unique(res.wide$k))))
res.wide$selProp.label <- factor(res.wide$selProp, levels=unique(res.wide$selProp), labels=paste0("selProp = ", unique(res.wide$selProp)))
res.wide$tau.label <- factor(res.wide$tau, levels=unique(res.wide$tau), labels=paste0("tau = ", unique(res.wide$tau)))


summ <- res.wide %>% group_by(condition, simBatch, k.label, delta, delta.label, selProp.label, tau.label, method) %>% summarise(
  meanEst		= mean(estimate, na.rm=TRUE),
  ME 			= mean(estimate - delta, na.rm=TRUE),
  RMSE			= sqrt(mean((estimate - delta)^2, na.rm=TRUE)),
  n.simulations = n()
)
```

## Method ##

Simulations were run with 10,000 replications for a selection of conditions. Then, these 10,000 runs were divided in 10 batches of 1000 simulations each. The following plots show points for each of the 10 batches. One can see that they are virtually identical, as the points of the different batches overlap.

## Variance in ES estimates between simulation batches

```{r echo=FALSE, fig.width=11, fig.height=8, warning=FALSE}
ggplot(summ, aes(x=method, y=meanEst, color=simBatch, shape=factor(delta.label))) + geom_point() + geom_hline(aes(yintercept=delta), linetype="dotted") + facet_grid(selProp.label~k.label~tau.label) + coord_flip(ylim=c(-0.5, 1))
```


## Variance in RMSE between simulation batches

```{r echo=FALSE, fig.width=11, fig.height=8, warning=FALSE}
ggplot(summ, aes(x=method, y=RMSE, color=simBatch, shape=delta.label)) + geom_point() + facet_grid(selProp.label~k.label~tau.label) + coord_flip(ylim=c(-.8, .8))
```
